Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-12-24 paper/main.tex
final cosmetic modifications

\begin{figure*}
 \setlength{\progwidth}{.28\linewidth}
  \centering
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void count_down (int x) {
  int a = x;
  if (a>0) {
    a = a-1;
    count_down(a);
  }
}
int copy (int x, int y) {
  if (x>0) {
    x = x-1;
    y = y+1;
    y=copy(x,y);
  };
  return y;
}
void main (int x,int y) {
  y = copy (x,y);
  count_down(y);
}
   \end{lstlisting}

@@

void main (int y, int z) {
  count_down(y,z);
}
   \end{lstlisting}

$1.33 + 0.67 |[z,y]|$
\\[.7\baselineskip]
      {\bf t39}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void produce () {
  while (x>0) {
    tick(-1); x=x-1; y=y+1;
  }
}
void consume () {
  while (y>0) {
    y=y-1; x=x+1; tick(1);
  }
}
void main (int y, int z) {
  consume(); produce(); consume();
}
   \end{lstlisting}

@@

$|\inter 0 x| + |\inter 0 y|$
\\[.7\baselineskip]
      {\bf Greatest Common Divisor}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void qsort(int a[], int lo, int hi) {
  int m1, m2, n;

@@

  n = nondet(); /* partition the array */
  assert( n > 0 );
  assert( lo + n <= hi );

@@

void main(int a[], int len) {
  qsort(a, 0, len);
}
   \end{lstlisting}

>>>>

\begin{figure*}
 \setlength{\progwidth}{.28\linewidth}
  \centering
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void count_down (int x) {
  int a = x;
  if (a>0) {
    a = a-1;
    count_down(a);
  }
}
int copy (int x, int y) {
  if (x>0) {
    x = x-1;
    y = y+1;
    y=copy(x,y);
  };
  return y;
}
void start (int x,int y) {
  y = copy (x,y);
  count_down(y);
}
   \end{lstlisting}

@@

void start (int y, int z) {
  count_down(y,z);
}
   \end{lstlisting}

$1.33 + 0.67 |[z,y]|$
\\[.7\baselineskip]
      {\bf t39}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void produce () {
  while (x>0) {
    tick(-1); x=x-1; y=y+1;
  }
}
void consume () {
  while (y>0) {
    y=y-1; x=x+1; tick(1);
  }
}
void start (int y, int z) {
  consume(); produce(); consume();
}
   \end{lstlisting}

@@

$|\inter 0 x| + |\inter 0 y|$
\\[.7\baselineskip]
      {\bf Greatest Common Divisor}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void qsort(
  int a[], int lo, int hi
) {
  int m1, m2, n;

@@

  n = nondet(); /* partition */
  assert( n > 0 );
  assert( lo + n <= hi );

@@

void start(int a[], int len) {
  qsort(a, 0, len);
}
   \end{lstlisting}
